---
title: "Cabbages"
author: "Cynthia Cornejo"
date: "06/05/2023"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->



```{r}
# Assuming you have the ggplot2 package installed
library(ggplot2)

# Create a box plot using ggplot2
ggplot(veggy, aes(x = Cult, y = VitC)) +
  geom_boxplot() +
  xlab("Cult") + ylab("VitC") +
  ggtitle("Box Plot of VitC by Cult") +
  theme(plot.title = element_text(hjust = 0.5, size = 16))

```


Observe the two boxes on the box plot. Above the bottom box is the larger one. Between the C39 and C52, there is a significant difference in the middle 50% of the method of higher box. Apart from each other, they are complete. With these 2 methods, we estimate finding a statistical difference. 



### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(VitC~Cult,data=veggy)
```

51 is the average amount of vitamin C39. Vitamin C52 is present in an average amount of 64.5. Boxes C52 and C39 do not overlap. The amounts give the numerical difference. 

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(VitC~Cult,data=veggy)
```

The likelihood of receiving the outcome we just did is. The number .000000003405 is extremely small. This is what we received as a result. Vitamin C39 is significantly lower than vitamin C52. Although there is very little chance that it will, it is feasible. It is necessary to disprove the theory. The methods differ. 


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

Today's lesson taught me how to develop a plot. I discovered using Chat GPT to get assistance with my box plot. I also added a comment following each plot or graphic. I developed the ability to interpret the T test results and communicate them in simple terms for everyone. 



